\documentclass{skrul-leadsheet}

\begin{document}
\begin{song}[transpose-capo=true]{title={Ziggy Stardust}, band={David Bowie}, year={1972}, key={G}}

\begin{intro}
\begin{tabular}[t]{@{}lllll}
|_{G} & | _{D} & |_{Cadd9} & | _{G/B} _{G/A} & | 4x
\end{tabular}
\end{intro}

\begin{verse}
^{G} Now Ziggy played guitar,
^{Bm}  Jamming good with Weird and ^{C}Gilly, \\
And the Spi^-{C†} - ^{B†}ders ^{C†} ^{C#†}from ^{D}Mars.
He played it left hand,^{G} \\
But made it too far.^{Em}
Became the ^{Am}special man, then we were ^{C}Ziggy's band.
\end{verse}

\begin{verse}
^{G} Ziggy really sang,
^{Bm}screwed up eyes and screwed down ^{C}hairdo, \\
Like some ^-{C†}cat ^{B†}from ^{C†}Ja - ^{C#†}pan. {^D}
He could lick 'em by smili^{G}ng, \\
He could leave them to ^{Em}hang.
They came on so ^{Am}loaded, man, well hung, ^{C}snow white tan....
\end{verse}

\begin{chorus}
^{Am} So w^{G5}here were the sp^{F5}iders, ^{G5†}
^{Am} While the ^{G5}fly tried to br^{F5}eak our balls? ^{G5†} \\
^{Am} Just the ^{G5}beerlight to gu^{F5}ide us,
 so ^{G5†}we ^{D}bitched about his ^{D}fans and should we ^{E}crush his sweet hands?
\end{chorus}

\begin{interlude}
\begin{tabular}[t]{@{}lllll}
|_{G} & | _{D} & |_{Cadd9} & | _{G/B} _{G/A} & | 2x
\end{tabular}
\end{interlude}

\begin{verse}
^{G} Ziggy played for time,
^{Bm}jiving us that we were voo^{C}doo. \\
The ^{C†}kids ^{B†}were ^{C†}just ^{C#†} ^{D}crass,
He was the ^{G}nazz, \\
With God given ^{Em}ass.
He took it ^{Am}all too far, but, boy, could he ^{C}play guitar!
\end{verse}

\begin{chorus}
^{Am} Making ^{G5}love with his ^{F5}ego, ^{G5†}
^{Am} Ziggy ^{G5}sucked up in^{F5}to his mind, ^{G5†} \\
^{Am} Like a ^{G5}leper Mess^{F5}iah,
When ^{G5†}the ^{D}kids had killed the ^{D}man I had to ^{E}break up the band!
\end{chorus}

\begin{interlude}
\begin{tabular}[t]{@{}lllll}
|_{G} & | _{D} & |_{Cadd9} & | _{G/B} _{G/A} & | 2x
\end{tabular}
\end{interlude}

\begin{outro}
^{G} Oh Yeah... ^{D}      ^{Cadd9}     ^{G/B}    ^{G/A}ooo. \\
^{G} ^{D}        ^{Cadd9*} Ziggy played guit^{G*}ar!
\end{outro}

\end{song}
\end{document}
