\documentclass{skrul-leadsheet}
\begin{document}
\begin{song}[transpose-capo=true]{title={Hold Me Now}, band={Thompson Twins}, year={1974}, key={C}}

\begin{intro}
\begin{tabular}[t]{@{}lllll}
|_{D} & |_{Bm} & |_{Cadd9} & |_{A7sus4} & | \\
\end{tabular}
\end{intro}

\begin{verse}
^{D}I have a picture p^{Bm}inned to my wall \\
An im^{Cadd9}age of you and of me and we're laughing, we're l^{A7sus4}oving it all \\
^{D}Look at our life now, t^{Bm}attered and torn \\
We f^{Cadd9}uss and we fight and delight in the tears that we ^{A7sus4}cry until dawn. Oh...
\end{verse}

\begin{chorus}
H^{D}old me now. Whoa, w^{Bm}arm my heart \\
S^{Cadd9}tay with me. Let ^{A7sus4}loving start, let loving start
\end{chorus}
 
\begin{verse}
You s^{D}ay I'm a dreamer. We're t^{Bm}wo of a kind \\
B^{Cadd9}oth of us searching for some perfect world we know ^{A7sus4}we'll never find  \\
So per^{D}haps I should leave here, yeah, ^{Bm}go far away \\
But you k^{Cadd9}now that there's nowhere that I'd rather be than with ^{A7sus4}you here today. Oh...
\end{verse}

\begin{chorus}
\instruction{Repeat Chorus 2x}
\end{chorus}

\begin{bridge}
Whoah woah wo^{Bb}ah... ^{Cadd9} \\
_{Bb} _{C} \\
_{Bb} _{C} \\
_{Bb} _{C}
\end{bridge}

\begin{verse}
You ^{D}ask if I love you. Well, w^{Bm}hat can I say? \\
You k^{Cadd9}now that I do and that this is just one of those g^{A7sus4}ames that we play \\
So I'll s^{D}ing you a new song. Please don't ^{Bm}cry anymore \\
And then a^{Cadd9}sk your forgiveness though I don't know just what I'm ^{A7sus4}asking it for. Oh...
\end{verse}

\begin{chorus}
\begin{tabbing}
	
H^{D}old me now\= \hspace{140pt} Oh... \\
              \>(Hold me in your loving arms) \\
W^{Bm}arm my heart\= \\
              \>(Warm my cold and tired heart) \\
S^{Cadd9}tay with me\= \\
              \>(Oh, will you stay with me?) \\
Let l^{A7sus4}oving start, let loving start, whoa
\instruction{Repeat to fade}
\end{tabbing}
\end{chorus}

\end{song}
\end{document}
