\documentclass{skrul-leadsheet}

\begin{document}
\begin{song}[transpose-capo=true]{title={The Middle}, band={Jimmy Eat World}, year={2001}, key={D}}

\newcommand{\itjusttakessometime}{%
\begin{chorus}
It just ^{D}takes some time, little girl you're in the middle ^{A}of the ride \\
Everything, everything will ^{G}be just fine, everything, everything will ^{D}be all right (all right)
\end{chorus}%
}

\newcommand{\itjusttakessometimerepeat}{%
\begin{chorus}
It just ^{D}takes some time, little girl you're in the middle ^{A}of the ride \\
Everything, everything will ^{G}be just fine, everything, everything will ^{D}be all right (all right) \instruction {Repeat}
\end{chorus}%
}

\begin{intro}
\begin{tabular}[t]{@{}lllll}
|_{D} & | _{A} & |_{G} & | _{D} & |
\end{tabular}
\end{intro}

\begin{verse}
^{D}Hey, don't write yourself off ^{A}yet. \\
It's only in your head you ^{G}feel left out or looked down ^{D}on. \\
Just try your ^{D}best, try everything you ^{A}can. \\
And don't you worry what they ^{G}tell themselves when you're ^{D}away.
\end{verse}

\itjusttakessometime

\begin{verse}
^{D}Hey, you know they're all the ^{A}same. \\
You know you're doing better ^{G}on your own, so don't buy ^{D}in. \\
Live right ^{D}now. Yeah, just be your^{A}self. \\
It doesn't matter if it's ^{G}good enough for someone ^{D}else.
\end{verse}

\itjusttakessometimerepeat

\begin{solo}
\begin{tabular}[t]{@{}lllll}
|_{A} & | _{D} & |_{A} & | _{D} & | \\
|_{G} & | _{D} & |_{A} & | _{A} & | \\
\end{tabular}
\end{solo}

\begin{verse}
^{D}Hey, don't write yourself off ^{A}yet. \\
It's only in your head you ^{G}feel left out or looked down ^{D}on. \\
Just do your ^{D}best, do everything you ^{A}can. \\
And don't you worry what the ^{G}bitter hearts are gonna ^{D}say.
\end{verse}

\itjusttakessometimerepeat

\end{song}
\end{document}
