\begin{verse}
^{A#*} How high's the water, mama? ^{A#}Two feet high and rising \\
^{A#}How high's the water, papa? She said it's ^{A#}two feet high and rising \\

We can ^{A#}make it to the road in a homemade boat \\
That's the ^{D#}only thing we got left that'll float \\
It's ^{F}already over all the wheat and the oats, ^{F}two feet ^{-}high and ^{A#}rising ^{-} \hspace{20pt} ^{C#}
\end{verse}

\begin{verse}
^{C#}How high's the water, mama? ^{C#}Three feet high and rising \\
^{C#}How high's the water, papa? She said it's ^{C#}three feet high and rising \\

Well, the ^{C#}hives are gone, I've lost my bees \\
The ^{F#}chickens are sleeping in the willow trees \\
^{G#}Cow's in water up past her knees, ^{G#}three feet ^{-}high and ^{C#}rising ^{-} \hspace{20pt} ^{D#}
\end{verse}

\begin{verse}
^{D#}How high's the water, mama? ^{D#}Four feet high and rising \\
^{D#}How high's the water, papa? She said it's ^{D#}four feet high and rising \\

^{D#}Hey, come look through the window pane \\
The ^{G#}bus is coming, it's going to take us to the train \\
^{A#}Looks like we'll be blessed with a little more rain, ^{A#}four feet ^{-}high and ^{D#}rising  \hspace{20pt} ^{F}
\end{verse}

\begin{verse}
^{F}How high's the water, mama? ^{F}Five feet high and rising \\
^{F}How high's the water, papa? She said it's ^{F}five feet high and rising \\

Well, the ^{F}rails are washed out north of town \\
^{A#}We got to head for higher ground \\
We ^{C}can't come back till the water comes down, ^{C}five feet ^{-}high and ^{F}rising \\
\end{verse}

\begin{outro}
Well it's ^{F*}five feet high and rising
\end{outro}
