\documentclass{skrul-leadsheet}
\begin{document}
\begin{song}[transpose-capo=true]{title={I've Been Everywhere}, band={Johnny Cash}, year={1996}, key={E}, note={written by Geoff Mack in 1959}}
 
\begin{intro}
\begin{tabular}[t]{@{}ll}
|_{E} & | \\
\end{tabular}
\end{intro}

\begin{intro}
I was ^{E*}totin' my pack along the long dusty Winnemucca road, \\
When ^{E*}along came a semi with a high an' canvas-covered load. \\
"If you're ^{A*}goin' to Winnemucca, Mack, with me you can ride." \\
And so I ^{E*}climbed into the cab and then I settled down inside. \\
He ^{B7*}asked me if I'd seen a road with so much dust and sand. \\
And I said, "^{E*}Listen, I've traveled every road in this here land!"
\end{intro} 

\begin{chorus}
^{E}I've been everywhere, man. \\
^{E}I've been everywhere, man. \\
^{A}Crossed the deserts bare, man. \\
I've ^{E}breathed the mountain air, man. \\
Of ^{B7}travel I've had my share, man. \\
I've been every^{E}where.
\end{chorus} 

\begin{verse}
I've been to ^{E}Reno, Chicago, Fargo, Minnesota, \\
^{E}Buffalo, Toronto, Winslow, Sarasota, \\
^{A}Wichita, Tulsa, Ottawa, Oklahoma, \\
^{E}Tampa, Panama, Mattawa, La Paloma, \\
^{B7}Bangor, Baltimore, Salvador, Amarillo, \\
^{E}Tocapillo, Baranquilla, and Perdilla, I'm a killer.
\end{verse} 

\begin{chorus}
\instruction{Repeat Chorus}
\end{chorus}

\begin{verse}
I've been to ^{E}Boston, Charleston, Dayton, Louisiana, \\
^{E}Washington, Houston, Kingston, Texarkana, \\
^{A}Monterey, Faraday, Santa Fe, Tallapoosa, \\
^{E}Glen Rock, Black Rock, Little Rock, Oskaloosa, \\
^{B7}Tennessee, Hennessey, Chicopee, Spirit Lake, \\
^{E}Grand Lake, Devils Lake, Crater Lake, for Pete's sake.
\end{verse} 

\begin{chorus}
\instruction{Repeat Chorus}
\end{chorus}

\begin{verse}
I've been to ^{E}Louisville, Nashville, Knoxville, Ombabika, \\
^{E}Schefferville, Jacksonville, Waterville, Costa Rica, \\
^{A}Pittsfield, Springfield, Bakersfield, Shreveport, \\
^{E}Hackensack, Cadillac, Fond du Lac, Davenport, \\
^{B7}Idaho, Jellico, Argentina, Diamantina, \\
^{E}Pasadena, Catalina, see what I mean-a.
\end{verse} 

\begin{chorus}
\instruction{Repeat Chorus}
\end{chorus}

\begin{verse}
I've been to ^{E}Pittsburgh, Parkersburg, Gravelbourg, Colorado, \\
^{E}Ellisburg, Rexburg, Vicksburg, Eldorado, \\
^{A}Larimore, Admore, Haverstraw, Chatanika, \\
^{E}Chaska, Nebraska, Alaska, Opelika, \\
^{B7}Baraboo, Waterloo, Kalamazoo, Kansas City, \\
^{E}Sioux City, Cedar City, Dodge City, what a pity.
\end{verse} 

\begin{chorus}
\instruction{Repeat Chorus}
\end{chorus}

\begin{outro}
^{E}I've been everywhere.
\end{outro}

\end{song}
\end{document}