\documentclass{skrul-leadsheet}

\begin{document}

\begin{song}[transpose-capo=true]{title={To Be With You}, band={Mr. Big}, year={1991}, key={C#m}}

\begin{verse}
^{C#m} Hold on little ^{E}girl.  ^{Asus2}Show me what he's ^{E}done to you. \\
^{C#m} Stand up little ^{E}girl.  A ^{Asus2}broken heart can't ^{E}be that bad. \\
When ^{Asus2}it's through, it's ^{E}through.  ^{Asus2}Fate will twist the ^{E}both of you. \\
So ^{D}come on baby, ^{D}come on over. ^{B}Let me be the ^{B}one to show you.
\end{verse}

\begin{chorus}
\begin{tabbing}
^{E}I'm ^{E/F#}the  ^{E/G#}one    ^{E}who ^{Asus2}wants to ^{B}be with you ^{E} \hspace{.75in} \=
^{E}Deep ^{E/F#}inside ^{E/G#}  ^{E}I   ^{Asus2}hope you'll ^{B}feel it too. ^{E} \\
^{E}Waited  ^{E/F#}  ^{E/G#}on   ^{E}a   ^{Asus2}line of ^{B}greens and ^{C#m}blues \>
^{E}Just ^{E/F#}to  ^{E/G#}be  ^{E}the  ^{Asus2}next to    ^{B}be with     you. ^{E}
\end{tabbing}
\end{chorus}

\begin{verse}
^{C#m} Build up your ^{E}confidence so ^{Asus2}you can be on ^{E}top for once. \\
^{C#m}Wake up! Who ^{E}cares about ^{Asus2}little boys that ^{E}talk too much?  \\
I ^{Asus2}seen it all go ^{E}down.  Your ^{Asus2}game of love was ^{E}all  rained out.  \\
So ^{D}come on baby, ^{D}come on over.  ^{B}Let me be the ^{B}one to hold you.
\end{verse}

\begin{chorus}
\instruction{Repeat Chorus}
\end{chorus}

\begin{bridge}
^{Asus2} Why be alone when we can ^{C#m}be together baby? \\
^{G}You can make my life worthwhile, ^{G}I can make you start to  smile.	
\end{bridge}

\begin{solo}
\begin{tabular}[t]{@{}lllll}
|_{E} _{E/F#} _{E/G#} _{E} & | _{Asus2} & | _{B} & |  _{E} & | \\
|_{E} _{E/F#} _{E/G#} _{E} & | _{Asus2} & | _{B} & |  _{E} & | \\
|_{E} _{E/F#} _{E/G#} _{E} & | _{Asus2} & | _{B} & |  _{C#m} & | \\
|_{E} _{E/F#} _{E/G#} _{E} & | _{Asus2} & | _{B} & |  _{E} & | \\
\end{tabular}
\end{solo}

\begin{prechorus}
When ^{Asus2}it's through, it's ^{E}through. ^{Asus2}Fate will twist the  ^{E}both of you. \\
So ^{D}come on baby, ^{D}come on over.  ^{B}Let me be the ^{B*}one to show you.
\end{prechorus}

\begin{chorus}
\begin{tabbing}
^{G}I'm ^{G/A}the  ^{G/B}one    ^{G}who ^{Cadd9}wants to ^{D}be with you ^{G}  \hspace{.75in} \=
^{G}Deep ^{G/A}inside ^{G/B}  ^{G}I   ^{Cadd9}hope you'll ^{D}feel it too. ^{G} \\
^{G}Waited  ^{G/A}  ^{G/B}on   ^{G}a   ^{Cadd9}line of ^{D}greens and ^{Em}blues \>
^{G}Just ^{G/A}to  ^{G/B}be  ^{G}the  ^{Cadd9}next to    ^{D}be with     you. ^{G}
\end{tabbing}
\end{chorus}

\begin{chorus}
\instruction{Repeat Chorus (back to original key)}
\end{chorus}

\begin{outro}
^{E}Just ^{E/F#}to  ^{E/G#}be  ^{E}the  ^{Asus2}next to    ^{B}be with     you. ^{E7} 
\end{outro}


\end{song}
\end{document}
