\documentclass{skrul-leadsheet}
\begin{document}
\begin{song}[transpose-capo=true]{title={Brain Damage / Eclipse}, band={Pink Floyd}, year={1973}, key={}}

 
\begin{solo}
\begin{tabular}[t]{@{}lllll}
|_{D} & |_{D} & |_{D} & |_{D} & | \\
\end{tabular}
\end{solo}
 
 
\begin{verse}
^{D} The lunatic is on the ^{G7/D}grass.   \\
^{D} The lunatic is on the ^{G7/D}grass.   \\
^{D} Remembering games and ^{E/D}daisy chains and laughs. \\
^{A7}Got to keep the ^{A7}loonies on the ^{D}path.    ^{Dsus2}      \\

^{D}  The lunatic is in the hal^{G7/D}l.   \\
^{D}  The lunatics are in my ^{G7/D}hall. \\
^{D}  The paper holds their folded ^{E/D}faces to the floor \\
And ^{A}every day the ^{A7}paper boy brings ^{D}more.    ^{Dsus2}       ^{D7}    ^{D9}   \\
\end{verse}

\begin{chorus}
^{G}  And if the dam breaks open ^{A}many years too soon \\
And ^{C}if there is no room upon the ^{G}hill     \\
^{G}  And if your head explodes with ^{A7}dark forebodings too \\
I'll ^{C}see you on the dark side of the ^{G}moon.     ^{Bm7}     ^{Em7}     ^{A}   ^{A7}   \\
\end{chorus} 
 
\begin{verse}
^{D}  The lunatic is in my ^{G7/D}head.    (laughter) \\
^{D}  The lunatic is in my ^{G7/D}head     \\
^{D}  You raise the blade,^{E/D} you make the change \\
^{A7}  You re-arrange me 'till I'm sane^{D}.     ^{Dsus2}      \\

^{D}  You lock the door \\
And ^{E/D}throw away the key \\
There's ^{A7}someone in my head but it's not ^{D}me. ^{Dsus2}        ^{D7}    ^{D9}   \\
\end{verse} 
 
\begin{chorus}
^{G}  And if the cloud bursts, ^{A}thunder in your ear \\
^{C}  You shout and no one seems to hear^{G}. \\
And if the band you're in starts ^{A}playing diff^{A7}erent tune^{A}s \\
I'll ^{C}see you on the dark side of the moon^{G}.  ^{Bm7}     ^{Em}    ^{A7}   \\
\end{chorus} 


[Outro]
D      |G7        |D    |G7    |D      |E         |
A  A7  |D  Dsus2  |D    |E     |A  A7  |D  Dsus2  |
 
 
[Intro]
|D  D7  |Bb  A A7|
 
\begin{outro}
^{D}All that you touch, and ^{D7}all that you see, ^{Bb}all that you taste,^{A7}  all you feel. \\
And ^{D}all that you love, and ^{D7}all that you hate, ^{Bb}all you distrust,^{A7}  all you save. \\
And ^{D}all that you give, and ^{D7}all that you deal, and ^{Bb}all that you buy, \\
beg, ^{A7}borrow or steal. \\
And ^{D}all you create, and ^{D7}all you destroy, and ^{Bb}all that you do, \\
and ^{A7}all that you say. \\
And ^{D}all that you eat, and ^{D7}everyone you meet, and ^{Bb}all that you slight, \\
and ^{A7}everyone you fight. \\
And ^{D}all that is now, and ^{D7}all that is gone, and ^{Bb}all that's to come, \\
and ^{A7}everything under the ^{D}sun is in tune, \\
But the ^{D7}sun is eclipsed by the ^{Bb}moo- ^{D}n.
\end{outro} 

\end{song}
\end{document}
