\documentclass{skrul-leadsheet}

\begin{document}
\begin{song}{title={Breathe / Time}, band={Pink Floyd}, year={1973}, key={Em F#m Em}}

\begin{intro}
\begin{tabular}[t]{@{}lll}
|_{Em} & | _{A7} | 2x
\end{tabular}
\end{intro}

\begin{verse}
^{Em}Breathe, breathe in the ^{A7}air, ^{Em}don't be afraid to ^{A7}care \\
^{Em}Leave, don't leave ^{A7}me, ^{Em}look around and choose your ^{A7}own ground
\end{verse}

\begin{chorus}
^{Cmaj7}Long you live and high you fly, ^{Bm7}smiles you'll give and tears you'll cry \\
^{Fmaj7}All you touch and all you see, ^{G}is all your life will ^{D7#9}ever ^{D7b9}be
\end{chorus}

\begin{verse}
^{Em}Run, rabbit ^{A7}run, ^{Em}dig that hole, forget the ^{A7}sun \\
^{Em}And when at last the work is ^{A7}done, ^{Em}don't sit down it's time to dig a^{A7}nother one.
\end{verse}

\begin{chorus}
^{Cmaj7}For long you live and high you fly, ^{Bm7}but only if you ride the tide \\
^{Fmaj7}And balanced on the biggest wave, ^{G}you race towards an ^{D7#9}early ^{D7b9}grave
\end{chorus}

\begin{interlude}
\begin{tabular}[t]{@{}lllll}
|_{Em} & | single note _{E} hammer on _{F} & | _{F#m} & | 4x
\end{tabular}
\end{interlude}

\begin{verse}
^{F#m}Ticking away the moments that make up a ^{A}dull day \\
^{E}Fritter and waste the hours in an offhand ^{F#m}way \\
^{F#m}Kicking around on a piece of ground in your ^{A}hometown \\
^{E}Waiting for someone or something to show you the ^{F#m}way
\end{verse}

\begin{chorus}
^{Dmaj7}Tired of lying in the sunshine, ^{Amaj7}staying home to watch the rain \\
^{Dmaj7}You are young and life is long, and ^{Amaj7}there is time to kill today \\
 ^{Dmaj7} And then one day you find, ^{C#m7} ten years have got behind you \\
^{Bm7}No one told you when to run ... ^{E} You missed the starting gun
\end{chorus}

\newpage

\begin{verse}
And you ^{F#m}run and you run to catch up with the Sun, but it's ^{A}sinking; \\
^{E}Racing around to come up behind you a^{F#m}gain. \\
The ^{F#m}sun is the same in a relative way, but you're ^{A}older, \\
^{E}shorter of breath, and one day closer to ^{F#m}death.
\end{verse}

\begin{chorus}
^{Dmaj7}Every year is getting shorter, ^{Amaj7}never seem to find the time. \\
^{Dmaj7}Plans that either come to naught, or ^{Amaj7}half a page of scribbled lines. \\
^{Dmaj7}Hanging on in quiet despe^{C#m7}ration is the English way. \\
The ^{Bm7}time is gone, the song is over. ^{Bm7}Thought I'd something ^{F/B}more to say.
\end{chorus}

\begin{interlude}
\begin{tabular}[t]{@{}lll}
|_{Em} & | _{A7} | 2x
\end{tabular}
\end{interlude}

\begin{verse}
^{Em}Home, home ^{A7}again, ^{Em}I like to be here when I ^{A7}can \\
^{Em}When I come home cold and ^{A7}tired, ^{Em}it's good to warm my bones besides the ^{A7}fire
\end{verse}

\begin{chorus}
^{Cmaj7}Far away, across the field ^{Bm7}Tolling on the iron bell \\
^{Fmaj7}Calls the faithful to their knees ^{G} To hear the softly ^{D7#9}spoken ^{D7b9}magic ^{Em}spell
\end{chorus}


\end{song}
\end{document}
