\documentclass{skrul-leadsheet}
\begin{document}
\begin{song}[transpose-capo=true]{title={Don't Carry It All}, band={The Decemberists}, year={2011}, key={G}}

\begin{intro}
\begin{tabular}[t]{@{}lllll}
|_{G} & |_{G} & |_{G} & |_{Em} - _{D} & | \instruction{Repeat 2x} \\
\end{tabular}
\end{intro}
 
\begin{verse}
^{G}Here we come to a ^{G}turning of the ^{G}season.       ^{Em} ^{-} ^{D}  \\
^{G}Witness to the ^{G}arc to-ward the ^{G}sun.             ^{Em} ^{-} ^{D}  \\
A ^{G}neighbors blessed ^{G}burden within ^{G}reason.      ^{Em} ^{-} ^{D}  \\
Be^{G}comes a burden ^{G}borne of all in ^{G}one, and ^*{Em}nobo ^{-}dy, ^{D}nobody ^{(C)}knows
\end{verse} 
 
\begin{chorus}
\begin{tabbing}
^{C} Let the ^{C}yoke fall from our ^{G}shoulders. ^{G}
\hspace{20pt} \=^{C} Don't carry it al^{C}l, don't carry it ^{Em}all.   ^{Em} ^{-}  ^{D}   \\
^{C} We are ^{C}all our hands and ^{G}holders. ^{G}
\>Beneath this ^{Bm}bold and ^{Bm}brilliant ^{C}sun, ^{C}this I swear to ^{(G)}all.
\end{tabbing}
\end{chorus} 

\begin{postchorus}
\begin{tabular}[t]{@{}lllll}
|_{G} & |_{G} & |_{G} & |_{Em} - _{D} & | \instruction{Harmonica!} \\
\end{tabular}
\end{postchorus}
 
\begin{verse}
^{G}Monument to bu^{G}ild beneath the ^{G}arbors.          ^{Em} ^{-} ^{D}  \\
^{G}Upon a plinth that ^{G}towers toward the ^{G}trees.    ^{Em} ^{-} ^{D}  \\
Let ^{G}every vessel pi^{G}tching hard to ^{G}starboard.   ^{Em} ^{-} ^{D}  \\
^{G}Lay it's head on ^{G}summer's freckled k^{G}nees, and ^*{Em}nobo ^{-}dy, ^{D}nobody ^{(C)}knows
\end{verse} 
 
\begin{chorus}
\instruction{Repeat chorus}
\end{chorus} 

\begin{postchorus}
^{G} ^{G} ^{G} And ^{Em}this ^{-}I ^{D}swear to a^{G}ll. ^{G} ^{G} ^{Em} ^{-} ^{D}
\end{postchorus}
 
\begin{bridge}
And ^{Bm*}there a wreath of ^{N.C.}trillium and ^{C*}ivy; ^{N.C.}
^{Bm*}Laid upon the ^{N.C.}body of the ^{Em*}boy. ^{N.C.} \\
^{Bm*}Lazy will the ^{N.C.}loam come from it's ^{C*}hiding; ^{N.C.}
^{Am*}Return this quiet ^{N.C.}searcher to the ^{D*}soil ^{N.C.}
\end{bridge}
 
\begin{verse}
So ^{G}raise a glass to ^{G}turnings of the ^{G}season.            ^{Em} ^{-} ^{D}  \\
And ^{G}watch it as it ^{G}arcs to-wards the ^{G}sun.               ^{Em} ^{-} ^{D}  \\
And you must ^{G}bare your neighbors ^{G}burden within ^{G}reason. ^{Em} ^{-} ^{D}  \\
And your ^{G}labors will be ^{G}borne when all is ^{G}done, and ^*{Em}nobo ^{-}dy, ^{D}nobody ^{(C)}knows
\end{verse} 

\begin{chorus}
\instruction{Repeat chorus}
\end{chorus} 

\begin{outro}
^{G} ^{G} ^{G} And ^{Em}this ^{-}I ^{D}swear to a^{(G)}ll. \instruction{Repeat 2x} \\
^{G} ^{G} ^{G} And ^{Em}this ^{-}I ^*{D}sweeee ^{G}eear to all, ^{G} to all, to ^{G}all, to ^*{Em}allllll ^{-}l...    ^{D} ^{G*}
\end{outro}

\end{song}
\end{document}