\begin{intro}
^{Gm7}Is this the real life? ^{C7}Is this just fantasy? \\
^*{F7}Caugh ^{-}t in a ^*{Cm7*}land ^{F7*}slide,
No e^{A#}scape from reality \\
^{Gm}Open your eyes,
look ^{A#7}up to the skies \\
And se^{D#}e  \\
^{Cm}I'm just a poor boy, ^{F7}I need no sympathy \\
Because I'm ^{B*}easy ^{A#*}come, ^{A*}easy ^{A#*}go,
^{B*}little ^{A#*}high, ^{A*}little ^{A#*}low \\
^{D#}Any wa^{-}y the ^{A#/D}wind blows, do^{Dbdim7}esn't rea^{-}lly ma^{F7/C}tter to me, \\
^{F7/C} To ^{A#}me... ^{A#}
\end{intro}
 
\begin{verse}
^{A#}Mama, just k^{Gm}illed a man, \\
Put a ^{Cm}gun against his head, 
pulled my ^{Cm}trigger, no^{-}w he's d^{F}ead, \\
^{A#}Mama, life had j^{Gm}ust begun, \\
But ^{Cm}now I've go^{-}ne and ^{Cm/B*}thrown it ^{Cm/A#*}all ^{Cm/A}away ^{-} ^{Cm/G#*} ^{Cm/G*}    \\
^*{D#}Mam ^{-}a o^*{A#*}ooo ^{Cm}h, \\
Didn't ^{Fm}mean to make you cry,
if ^{A#}I'm not back again \\
This time tomo^{D#}rrow,
c^{-}arry ^{A#}on, carry o^{Cm}n, as i^{-}f n^{G#m}othing really matte^{D#}rs ^{A#} ^{A#}
\end{verse}
 
\begin{verse}
^{A#}Too late, my t^{Gm}ime has come, \\
Sends ^{Cm}shivers down my spine,
body's ^{Cm}aching al^{-}l the ti^{F}me, \\
^{A#}Goodbye everybody - I've g^{Gm}ot to go \\
Gotta ^{Cm}leave yo^{-}u all be^{Cm/B*}hind and ^{Cm/A#*}face ^{Cm/A} the tru^{-}th ^{Cm/G#*} ^{Cm/G*}    \\
^*{D#}Mam ^{-}a o^*{A#*}ooo ^{Cm}h, (any way the wind blows) \\
^{Fm}I don't want to die, \\
I ^{A#}sometimes wish I'd never been born at al^{(D#)}l
\end{verse} 
 
\begin{solo}
\begin{tabular}[t]{@{}lllll}
|_{D#} _{A#} & |_{Cm} & |_{Fm} & |_{A#} & | \\
|_{D#} _{A#} & |_{Cm} & |_{Fm} & |_{Db} _{Db} _{C} _{B} _{A#} & | \\
\end{tabular}
\end{solo}
 
\begin{verse}
^{D}I ^{A}see a^{G#} little ^{A}silho ^{D}uetto ^{A} of ^{G#}a man, \\
^*{A}Scara ^{D}mouche, ^*{A}scara ^{D}mouche ^{A}, will y^{G#}ou do th^{A}e ^{D}Fan ^{A}dango \\
^{C#}Thunderbolt and ^{G#}lightning, v^{C}ery very f^{E}rightening ^{A*}me \\
^{N.\symbol{67}.}Gaileo, Galileo \\
^{N.\symbol{67}.}Galileo, Galileo \\
^{N.\symbol{67}.}Galileo, Figaro - Magnifico
\end{verse}

\begin{verse}
^{B*}I'm ^{A#*}just a ^{A*}poor ^{A#*}boy, ^{B*}no - ^{A#*}body ^{A*}loves ^{A#*}me. \\
^{G#}He's j^{D#}ust a po^{D#dim}or boy^{D#} from^{G#} a poor ^{D#}fami-l ^{D#dim}y. ^{D#}   \\
^{G#}Spare him his l^{D#/G}ife from this m^{F}onstrosit ^{A#}y.    ^{G#}    ^{D#/G}     ^{F#dim}       ^{Fm7}    \\
^{B}Easy ^{A#} come, ^{A}easy ^{A#} go, ^{B}will you^{A#} let me ^{A}go? ^{A#} Bis^{D#}mill ^{A#}ah! \\
^{D#}No, we w^{A#}ill not let you go.  Bi^{A#}smil ^{D#}lah! ^{A#}   \\
^{A#}We will not let you go.  B^{A#}ismi ^{D#}llah ^{A#}!  We w^{A#}ill not let you go. \\
^{A#}Will not let you go.  W^{A#}ill not let you go. Ahhhhhh^{F#7}hhh \\
^{Bm}No, ^{A}no, ^{D}no, ^{C#}no, ^{F#}no, ^{A#}no, ^{D#}no.  ^{N.\symbol{67}.}Oh, mama mia, mama mia \\
Mama ^{D#}mia, let me g^{A#}o.  Beel^{D#}zebub ^{G#} has a devi^{D}l put aside^{Gm} for me, ^{A#}
\end{verse}
 
\begin{solo}
\begin{tabular}[t]{@{}lllll}
|_{D#} & |_{D#} & |_{D#} & |_{F} & | \\
\end{tabular}
\end{solo}

\begin{verse}
^{A#}  So you think you can stone me and s^{D#}pit in my ey^{A#}e    ^{Db}   \\
^{A#}  So you think you can love me and l^{D#}eave me to di^{G#}e  \\
^{Fm}Oh, ^{A#}baby - ^{Fm}can't do this to me, b^{A#}aby \\
^{Fm}Just gotta get ^{A#}out - j^{Fm}ust gotta get r^{A#}ight outta he^{(D#)}re \\
\end{verse} 
 
[Riff/Instrumental]

\begin{solo}
\begin{tabular}[t]{@{}llllll}
|_{D#} & |_{D#} & |_{D#} & |_{F} & | _{N.\symbol{67}.} & | \\
|_{B#} & |_{G#} & |_{A#} & |_{A#} & | _{A#} & | \\
|_{D#} _{A#} & |_{Cm} _{G} _{Gm} & |_{G} _{Cm} _{A#} _{D#} & |_{D} _{Gm} & | _{G#} _{D#} & | \\
\end{tabular}
\end{solo}

\begin{outro}
^{Cm}Nothing really mat^{Gm}ters, \\
^{Cm}Anyone can ^{Gm}see, \\
^{Cm}Nothing really mat^{G#m}ters, n^{G#/A#}othing really matters to me, ^{(D#)}

\begin{solo}
\begin{tabular}[t]{@{}lllll}
|_{D#}  _{G#/D#} & |_{D#} _{D#dim} & | & | & | \\
|_{A#/D}  _{A#m/Db} & |_{C} _{Dbdim} & | _{C} _{C7} _{F} & | & | \\
\end{tabular}
\end{solo}

^{A#}Any w^{F}ay ^{A} the ^{Fdim/G#}wind   ^{Gm7}blows .^{F}..

\end{outro} 
