\documentclass{skrul-leadsheet}
\begin{document}
\begin{song}[transpose-capo=true]{title={Pour Some Sugar on Me}, band={Def Leppard}, year={1987}, key={C#m}}

\begin{intro}
Step inside, walk this way, you and me babe, hey hey! \\

\begin{tabular}[t]{@{}lllll}
|_{C#5} & |_{C#5} & |_{C#5} & |_{C#5} & | \instruction{intro riff} \\
|_{C#5} & |_{C#5} & |_{C#5} & |_{C#5} - _{C#5*} & | \instruction{intro riff} \\
\end{tabular}
\end{intro}

\begin{verse}
^{N.C.}Love is like a bomb, baby, ^{N.C.}c'mon get it on,
^{N.C.}livin' like a lover with a ^{N.C.}radar phone \\
^{N.C.}Lookin' like a tramp, like a ^{N.C.}video vamp,
^{N.C.}demolition woman, can I ^{N.C.}be your man? \\
 (Your ^{C#5}man) \hspace{20pt} ^{C#5*} \hspace{20pt} ^{C#5} \hspace{20pt} ^{C#5*}
\end{verse} 

\begin{verse}
^{C#5}Razzle 'n' a dazzle 'n' a ^{C#5*}flash a little light,
^{C#5}television lover, baby, ^{C#5*}go all night \\
^{C#5}Sometime, anytime, ^{C#5*}sugar me sweet,
^{C#5}little miss a-innocent ^{C#5*}sugar me \\
Yeah ^{C#5}oh,  \hspace{20pt} ^{C#5*} yeah ^{C#5}oh   \hspace{20pt}^{C#5*} C'mon...
\end{verse} 

\begin{prechorus}
^{F#}   ^{C#m}Take a ^{B}bottle, ^{F#}   ^{C#m}shake it ^{B}up \\
^{E}   ^{B}Break the ^{A}bubble, ^{E}   ^{A}break it ^{B}up
\end{prechorus}

\begin{chorus}
^{E}Pour some ^{A}sugar on ^{B}me, ooh, in the ^{B}name of love \\
^{E}Pour some ^{A}sugar on ^{B}me, c'mon, ^{B}fire me up \\
^{E}Pour your ^{A}sugar on ^{B}me, oh, I can't ^{B}get enough \\
^{C#5*} I'm hot, sticky sweet, from my head to my feet, yeah
\end{chorus} 

\begin{interlude}
\instruction{Repeat Intro}	
\end{interlude}

\begin{verse}
Listen! ^{N.C.}Red light, yellow light, ^{N.C.}green-a-light go!
^{N.C.}Crazy little woman in a ^{N.C.}one man show \\
^{N.C.}Mirror queen, mannequin, ^{N.C.}rhythm of love,
^{N.C.}sweet dream, saccharine, ^{N.C.}loosen up \\
(Loosen ^{C#5}up) \hspace{20pt} ^{C#5*} \hspace{20pt} Loosen ^{C#5}up \hspace{20pt} ^{C#5*}

\end{verse}
 
\begin{verse}
You gotta ^{C#5}squeeze a little, squeeze a little, ^{C#5*}tease a little more, ^{C#5}easy operator come a ^{C#5*}knockin' on my door \\ 
^{C#5}Sometime, anytime, ^{C#5*}sugar me sweet, ^{C#5}little miss innocent ^{C#5*}sugar me \\
Yeah ^{C#5}oh,  \hspace{20pt} ^{C#5*} yeah ^{C#5}oh   \hspace{20pt}^{C#5*} Give a little more
\end{verse}

\begin{prechorus}
\instruction{Repeat Prechorus}	
\end{prechorus}

\begin{chorus}
\instruction{Repeat Chorus}	
\end{chorus}

\begin{solo}
\begin{tabular}[t]{@{}lllll}
|_{D} & |_{D*} & |_{D} & |_{D*} & | \\
|_{D} & |_{D} & |_{D} & |_{D} & | \\
|_{E} & |_{E*} & |_{E} & |_{D*} & | \\
|_{D} & |_{D} & |_{D} & |_{D} & | \\
|_{E} & |_{E*} & |_{E} & |_{E*} & | \\
\end{tabular}
\end{solo} 

\begin{bridge}
\instruction{Drums only} \\
You got the peaches, I got the cream, sweet to taste, saccharine \\
'Cause I'm hot, hot, so hot, sticky sweet, from my head, my head, to my feet \\
^{E} ^{E*} Do you take sugar? ^{E} ^{E*} One lump or two?
\end{bridge} 

\begin{prechorus}
\instruction{Repeat Prechorus}	
\end{prechorus}
 
\begin{outro}
^{E}Pour some ^{A}sugar on m^{B}e, ooh, in the ^{B}name of love \\
^{E}Pour some ^{A}sugar on m^{B}e, c'mon, ^{B}fire me up \\
^{E}Pour your ^{A}sugar on m^{B}e, oh, I ^{B}can't get enough \\
^{E}Pour some ^{A}sugar on m^{B}e, ooh, in the ^{B}name of love \\
^{E}Pour some ^{A}sugar on m^{B}e, get it on, ^{B}come get it on \\
^{E}Pour your ^{A}sugar on m^{B}e, whoaaaaaaaaa^{B}wooahooo \\
^{E}Pour some ^{A}sugar on m^{B}e, y^{B}eah! Sugar me! ^{E} ^{A} ^{B}
\end{outro}

\end{song}
\end{document}