\documentclass{skrul-leadsheet}
\begin{document}
\begin{song}[transpose-capo=true]{title={Fire on the Mountain}, band={Grateful Dead}, year={1978}, key={B}, note={Solo in B mixolydian (E major)}}
\begin{intro}
\begin{tabular}[t]{@{}lll}
|_{B} & |_{A} & | \instruction{Repeat as  necessary}
\end{tabular}
\end{intro}

\begin{verse}
^{B} Long distance runner, what you ^{A}standin' there for? \\
^{B} Get up, get out,          get ^{A}out of the door \\
^{B} You're playin' cold music on the ^{A}barroom floor \\
^{B} Drowned in your laughter and ^{A}dead to the core. \\
^{B} There's a dragon with matches that's ^{A}loose on the town \\
^{B} Takes a whole pail of water just to ^{A}cool him down
\end{verse} 

\begin{chorus}
^{B}Fire! fire on the ^{A}mountain! \instruction{Repeat 4x}
\end{chorus} 

\begin{verse}
^{B} Almost ablaze still you ^{A}don't feel the heat \\
^{B} It takes all you got just to ^{A}stay on the beat. \\
^{B} You say it's a livin', we all gotta ^{A}eat \\
^{B} But you're here alone, there's no ^{A}one to compete. \\
^{B} If mercy's a business, I ^{A}wish it for you \\
^{B} More than just ashes when your ^{A}dreams come true.
\end{verse}
\begin{chorus}
^{B}Fire! fire on the ^{A}mountain! \instruction{Repeat 4x}
\end{chorus}

\begin{solo}
\begin{tabular}[t]{@{}lll}
|_{B} & |_{A} & | \instruction{Repeat as  necessary}
\end{tabular}
\end{solo}

\begin{verse}
^{B} Long distance runner, what you ^{A}holdin' out for? \\
^{B} Caught in slow motion in a ^{A}dash for the door. \\
^{B} The flame from your stage has now ^{A}spread to the floor \\
^{B} You gave all you had. why you ^{A}wanna give more? \\
^{B} The more that you give, the ^{A}more it will take \\
^{B} To the thin line beyond which you ^{A}really can't fake
\end{verse} 

\begin{outro}
^{B}Fire! fire on the ^{A}mountain!  \instruction{Repeat and fade maybe more solos??}
\end{outro}

\end{song}
\end{document}