\documentclass{skrul-leadsheet}

\begin{document}
\begin{song}[transpose-capo=true]{title={Champagne Supernova}, band={Oasis}, year={1996}, key={A}}

\begin{intro}
\begin{tabular}[t]{@{}lllll}
|_{Asus2} & |_{Asus2/G} &  |_{Asus2/F#} & |_{Asus2/E} & | 2x
\end{tabular}
\end{intro}

\begin{verse}
^{Asus2}How many special people change?  ^{Asus2/G}How many lives are living strange? \\
^{Asus2/F#}Where were you while we were getting ^{Asus2/E}high? \\
 ^{Asus2} Slowly walking down the hall, ^{Asus2/G}faster than a cannon ball \\
^{Asus2/F#}Where were you while we were getting ^{Asus2/E}high?
\end{verse}

\begin{chorus}
Someday you will ^{Asus2}find me caught beneath the ^{Asus2/G}landsliii-hide \\
In a ^{Asus2/F#}champagne supernova in the ^{Asus2/E}sky \\
Someday you will ^{Asus2}find me caught beneath the ^{Asus2/G}landsliii-hide \\
In a ^{Asus2/F#}champagne supernova a ^{Asus2/E}champagne supernova in the
^{Asus2}sky ^{Asus2/G} ^{Asus2/F#} ^{Asus2/E}
\end{chorus}

\begin{verse}
%^{Asus2}Wake up the dawn and ask her why, a ^{Asus2/G}dreamer dreams she never dies \\
%^{Asus2/F#}Wipe that tear away now from your ^{Asus2/E}eye \\
%^{Asus2}Slowly walking down the hall, ^{Asus2/G}faster than a cannon ball \\
%^{Asus2/F#}Where were you while we were getting ^{Asus2/E}high?
Wake up the dawn and ask her why, a dreamer dreams she never dies \\
Wipe that tear away now from your eye \\
Slowly walking down the hall, faster than a cannon ball \\
Where were you while we were getting high?

\end{verse}

\begin{chorus}
Someday you will ^{Asus2}find me caught beneath the ^{G}landsliii-hide \\
in a ^{Dmaj7/F#}champagne supernova in the ^{E}sky \\
Someday you will ^{Asus2}find me caught beneath the ^{G}landsliii-hide \\
in a ^{Dmaj7/F#}champagne supernova a ^{E}champagne supernova
\end{chorus}

\begin{bridge}
Cos ^{G}people believe that they're ^{G}gonna get away for the ^{Asus2}summer  ^{Asus2} \\
But ^{G}you and I we live and die, the ^{D}world's still spinning round
we don't know ^{E}why, \\
^{E}Why, why, why ^{Asus2}why ^{Asus2/G} ^{Asus2/F#} ^{Asus2/E}
\end{bridge}

\begin{interlude}
\begin{tabular}[t]{@{}lllll}
|_{Asus2} & |_{Asus2/G} &  |_{Asus2/F#} & |_{Asus2/E} & |
\end{tabular}
\end{interlude}
        
\begin{verse*}
\instruction{Repeat Verse 1} \instruction{Repeat Chorus 2} \instruction{Repeat Bridge}
\end{verse*}

%\begin{interlude}
%[Interlude]
%
% A    G    F#m    F  G    A    G    F#m    F  G 
% why                                       Na Na
% A      G      F#m    F  G      A      G      F#m 
% Na, Na Na, Na Na,    Na Na     Na, Na Na, Na Na
%$ F  G   F  G   F  G   A        Asus2/G      Asus2/F#        Asus2/E 
% Na Na, Na Na, Na Na, Na
%  A      Asus2/G      Asus2/F#        Asus2/E 
%\end{interlude}

\begin{interlude}
\begin{tabular}[t]{@{}lllll}
|_{Asus2} & |_{Asus2/G} &  |_{Asus2/F#} & |_{Asus2/E} & |
\end{tabular}
\end{interlude}
	
\begin{verse}
%^{Asus2}How many special people change? ^{Asus2/G}how many lives are living strange? \\
%^{Asus2/F#}Where were you while we were getting ^{Asus2/E}high? \\
%We were getting ^{Asus2}high, we were getting ^{Asus2/G}high \\
%We were getting ^{Asus2/F#}high, we were getting ^{Asus2/E}high \instruction{Repeat last two lines three times, fading vocals on thrid}
How many special people change? How many lives are living strange? \\
Where were you while we were getting high? \\
We were getting high, we were getting high \\
We were getting high, we were getting high \instruction{Repeat last two lines three times, fading vocals on third}
\end{verse}

\begin{outro}
\begin{tabular}[t]{@{}llll}
|_{F} & |_{G} &  |_{A*} & |
\end{tabular}
\end{outro}

\end{song}
\end{document}
