\documentclass{skrul-leadsheet}
\begin{document}
\begin{song}[transpose-capo=true,transpose=-5]{title={Dreaming}, band={Blondie}, year={1979}, key={}}

\begin{intro}
\begin{tabular}[t]{@{}lllll}
|_{D} & |_{D} & |_{G} & |_{G} & | \\
\end{tabular}
\end{intro}

\begin{verse}
^{D}When I met you in the ^{G}restaurant, \\
^{D}you could tell I was no d^{G}ebutante \\
^{D}You asked me what's my p^{A}leasure, \\
"A movie or a ^{Em}measure?" \\
I'll have a cup of ^{G}tea and ^{A}tell you of my
\end{verse}

\begin{chorus}
^{D}Dreaming, ^{G}dreaming is free. \\
^{D}Dreaming, ^{G}dreaming is free.
\end{chorus}

\begin{verse}
^{D}I don't want to live on ^{G}charity. \\
^{D}Pleasure's real or is it ^{G}fantasy? \\
^{D}Reel to reel is living r^{A}arity, \\
people stop and ^{Em}stare at me, \\
We just walk on ^{G}by; we j^{A}ust keep on ^{D}dreaming
\end{verse}

\begin{bridge}
^{G}Feet feet, walking a two-mile, \\
^{G}Meet meet, meet me at the turnstile. \\
I ^{D}never met him, I'll ^{A}never forget him. \\
^{G}Dream, dream, even for a little while, \\
^{G}Dream, dream, filling up an idle hour, \\
^{D}Fade away, woo,    ^{A}radiate.
\end{bridge}

\begin{verse}
^{D}I sit by and watch the ^{G}river flow. \\
^{D}I sit by and watch the ^{G}traffic go. \\
^{D}Imagine something of your ^{A}very own; \\
something you can ^{Em}have and hold, \\
I'd build a road in ^{G}gold j^{A}ust to have some
\end{verse}

\begin{outro}
^{D}Dreaming, ^{G}dreaming is free. \\
^{D}Dreaming, ^{G}dreaming is free. \\
^{D}Dreaming, ^{G}dreaming is free. \\
^{D}          ^{G}Dreaming is free
\end{outro}
\end{song}
\end{document}