\documentclass{skrul-leadsheet}

\begin{document}

\begin{song}[transpose-capo=true]{title={Add It Up}, band={Violent Femmes}, year={1983}, key={C#m}}

\begin{intro}
\begin{tabular}[t]{@{}lllllll}
|_{C} & |_{G/B} & |_{F/A} & |_{F} & | _{G} & | _{C} & | \\
\end{tabular}
\end{intro}

\begin{verse}
^{B5}Why can't I get just one kiss, ^{B5}why can't I get just one kiss \\
^{A}Believe me there'd be some things that I ^{A}wouldn't miss \\
But I ^{B5*}look at your pants and I need a kiss

^{B5}Why can't I get just one screw, ^{B5}why can't I get just one screw \\
^{A}Believe me I'd know ^{A}what to do \\
But ^{B5*}something won't let me make love to you
\end{verse}

\begin{interlude}
\begin{tabular}[t]{@{}lllllll}
|_{B5} & |_{A} & | \\
\end{tabular}
\end{interlude}

\begin{verse}
^{B5}Why can't I get just one fuck, ^{B5}why can't I get just one fuck \\
^{A}I guess it's got something to do with luck \\
But I ^{B5*}waited my whole life for just one
\end{verse}

\begin{chorus}
^{B5}Day... after day... I get ^{A}angry... and I will ^{B5}say...  \\
That the day... is in my sight... when I take a ^{A}bow... and say good^{B5}night	
\end{chorus}

\begin{verse}
\instruction{Palm muted} \\
Oh, ma-mama, mama-mo-ma-mum,
have you kept your eye, your eye on your son? \\
I know you've had problems, you're not the only one,
when your sugar left, he left you on the run. \\

Oh, ma-mama, mama-mo-ma-mum,
take a look now at what your boy has done. \\
He's walking around like he's number one,
went downtown and you got him a gun. \\

So don't shoot, shoot, shoot that thing at me,
don't shoot, shoot, shoot that thing at me. \\
You know you've got my sympathy,
but don't shoot, shoot, shoot that thing at me. \\

So don't shoot, shoot, shoot that thing at me,
don't shoot, shoot, shoot that thing at me. \\
You know you've got my sympathy,
but don't shoot, shoot, shoot that thing at me.
\end{verse}

\begin{interlude}
	
\end{interlude}

\begin{verse}
\instruction{Palm muted} \\
Going down the kitchen at the top of the stairs, can I mix in with your affairs? \\
Share a smoke, make a joke, grasp and reach for a leg of hope. \\

Words to memorize, words hypnotize, words make my mouth exercise.  \\
Words all failed the magic prize; nothing I can say when I'm in your thighs. \\

Oh, ma-mama, mo-ma, mo-ma mother, I would love to love you, lover. \\
City is restless, it's ready to pounce, here in your bedroom, ounce-for-ounce. \\

Oh, ma-mama, mo-ma, mo-ma mother, I would love to love you, lover. \\
City is restless, it's ready to pounce, here in your bedroom, ounce-for-ounce. \\

I've given you a decision to make, things to lose, things to take. \\
Just as she's about ready to cut it up:
She says, "Wait a minute, honey, I'm gonna add it up!" \\

Add it up! Add it up! Add it up!
Day after day, I get angry and I will say
That the day is in my sight when I'll take a bow and say goodnight.

\end{verse}

\end{song}
\end{document}
