\documentclass{skrul-leadsheet}
\begin{document}
\begin{song}[transpose-capo=true]{title={It's Still Rock and Roll to Me}, band={Billy Joel}, year={1980}, key={C}}

\begin{intro}
\begin{tabular}[t]{@{}lllll}
|_{C} & |_{C} & |_{C} & |_{C} & | \\
\end{tabular}
\end{intro}

\begin{verse}
^{C} What's the matter with the ^{Em}clothes I'm wearing?
"Can't you ^{Bb}tell that your tie's too w^{F}ide?" \\
^{C} Maybe I should buy some ^{Em}old tab collars?
"Welcome ^{Bb}back to the age of ^{F}jive. \\
^{Em}  Where have you been hidin' ^{Am}out lately, honey?
You ^{Em}can't dress trashy till you ^{D}spend a ^{-}lot of ^{G}money."
\end{verse}

\begin{chorus}
^*{C}Every ^{-}body's ^{Em}talkin’ 'bout the ^{Bb}new so^{-}und,
^{F}funny, but it's ^{Am}still rock ^{-}and ^{G}roll to ^{C}me \hspace{20pt} ^{C}
\end{chorus}

\begin{verse}
^{C} What's the matter with the ^{Em}car I'm driving?
"Can't ^{Bb}tell it's out of ^{F}style?" \\
^{C} Should I get a set of ^{Em}white wall tires?
"Are you ^{Bb}gonna cruise the miracle ^{F}mile? \\
^{Em} Nowadays you can't be ^{Am}too sentimental,
your ^{Em}best bet's a true baby ^{D}blue C^*{-}ontine ^{G}ntal."
\end{verse}

\begin{chorus}
^{C}Hot fu^{-}nk, ^{Em}cool punk ^{Bb}even if ^{-} it's o^{F}ld junk,
it's ^{Am}still roc^{-}k and ^{G}roll to ^{C}me... ^{C}Oh...
\end{chorus}

\begin{bridge}
^{G} It doesn't matter what they ^{F}say in the papers,
'cause it's ^{E}always been the same old sc^{Am}ene   \\
There's a ^{G}new band in town
but you ^{F}can't get the sound \\
From a ^{E}story in a maga^{Ab}zine...
^{Eb}aimed at your average ^{F}teen ^{G*}
\end{bridge}

\begin{verse}
^{C} How about a pair of ^{Em}pink sidewinders
and a ^{Bb}bright orange pair of ^{F}pants? \\
^{C} "Well, you could really be a ^{Em}Beau Brummel baby,
if you ^{Bb}just give it half a ch^{F}ance \\
^{Em}  Don't waste your money on a ^{Am}new set of speakers,
you ^{Em}get more mileage from a ^{D}cheap ^{-}pair of ^{G}sneakers."
\end{verse}

\begin{chorus}
^{C}Next p^{-}hase, ^{Em}new wave, ^{Bb}dance ^{-}craze, ^{F}anyways
it's ^{Am}still roc^{-}k and ^{G}roll to ^{C}me \hspace{20pt} ^{C}
\end{chorus}

\begin{solo}
\begin{tabular}[t]{@{}lllll}
|_{G} & |_{F} & |_{E} & |_{Am} & | \\
|_{G} & |_{F} & |_{E7} & |_{Ab} & | \\
|_{Eb} & |_{F} & |_{G*} & |_{N.C.} & | \instruction{say oooooh on the _{G*}} \\
\end{tabular}
\end{solo}

\begin{verse}
^{C} What's the matter with the ^{Em}crowd I'm seeing?
"Don't you ^{Bb}know that they're out of ^{F}touch?" \\
^{C} Should I try to be a ^{Em}straight 'A' student?"
"If you ^{Bb}are, then you think too ^{F}much. \\
^{Em} Don't you know about the ^{Am}new fashion, honey?
^{Em}All you need are looks and a ^{D}whole ^{-}lotta ^{G}money."
\end{verse}

\begin{chorus}
It's the ^{C}next p^{-}hase, ^{Em}new wave, ^{Bb}dance ^{-}craze ^{F}anyways
it's ^{Am}still rock ^{-}and ^{G}roll to ^{C}me
\end{chorus}

\begin{outro}
^{C*}Everybody's ^{Em*}talking about the ^{Bb}new sound
^{F*}funny, but it's ^{G*}still rock and roll to me ^{C9*} woooo woo!
\end{outro}

\end{song}
\end{document}