\begin{intro}
\begin{tabular}[t]{@{}lllll}
|_{F#} & |_{.F#} _{B*} _{A*} & |_{F#} & |_{.F#} _{B*} _{A*} & |  \instruction{Repeat 2x} \\
\end{tabular}
\end{intro}
 
\begin{verse}
^{F#}I'm making plans for the day ^{.D}all of this is t^{.B}hrough,
^{B} Seeing my path and ^{B} hearing the song I'll s^{A*}ing and \\
\scalebox{0.99}[1.0]{^{F#}Food that I'll taste and all the ^{.D}drinks that I'll con^{.B}sume; ^{B}
Return the smile on ^{B} an unmasked friend, as we} ^{A*}take \\
^{F#}Streets I don't walk down 'cause I ^{.D}want to av^{.B}oid; ^{B}
Fighting temptation, ^{B} walk at a downtown ^{A*}pace and \\
\scalebox{0.98}[1.0]{^{F#}Trea-sure the crowds that once made me ^{.D}act so an^{.B}noyed;
^{B} Sometimes I wonder, ^{B} how long 'til I'm a ^{A}face in} ^{(F#)}one?
\end{verse} 

\begin{interlude}
\begin{tabular}[t]{@{}lllll}
|_{F#} & |_{.F#} _{B*} _{A*} & |_{F#} & |_{.F#} _{B*} _{A*} & |  \instruction{Repeat 2x} \\
\end{tabular}
\end{interlude}

\begin{verse}
^{F#}You'd be surprised to learn what ^{.D}you could bear to ^{.B}lose;
^{B} Wanting and needing, ^{B} not getting either one ^{A*}and \\
^{F#}Planning the future as if ^{.D}time is yours to ^{.B}choose;
^{B} Pick out a movie, ^{B} a sandwich from a s^{A*}creen, yea \\
^{F#}How many days in life will ^{.D}I spend under^{.B}ground?
^{B} Hours in total, ^{B} as many as it ^{A*}takes and \\
^{F#}How many ways of feeling ^{.D}lousy have I ^{.B}found?
^{B}Lately uncounted, ^{.B} I've found a
\end{verse} 
 
\begin{chorus}
^{.E}Reason to ^{F#}exist ^{.F#} \\
^{.E}Written on the ^{F#}tile ^{.F#} \\
^{.E}Of the platform ^{F#}wall ^{.F#} \\
^{.E}Begging not to ^{C#}go ext^{.B}inct, ^{.A}to all those who ^{(F#)}saw
\end{chorus} 

\begin{interlude}
\begin{tabular}[t]{@{}lllll}
|_{F#} & |_{.F#} _{B*} _{A*} & |_{F#} & |_{.F#} _{B*} _{A*} & |  \instruction{Repeat 2x} \\
\end{tabular}
\end{interlude}
 
\begin{verse}
^{F#}How many times now have I ^{.D}walked into that ^{.B}room;
^{B} With the day shining ^{B} through purple film? Comb^{A*}ining \\
^{F#}Sound from the corners that you ^{.D}use yourself to ^{.B}tune;
^{B} Like a piano, ^{B} well-tuned and walking s^{A*}lowly \\
^{F#}Socks on the carpet while some ^{.D}kid watches my ^{.B}shoes;
^{B} Feeling the sine like ^{B} a bolt of lightning, ^{A*}house of \\
^{F#}Dreams, you were once my cure for ^{.D}New York City ^{.B}blues;
^{B} Is this goodbye then? ^{.B} Will you be
\end{verse} 
 
\begin{chorus}
^{.E}On the other ^{F#}side? ^{.F#} \\
^{.E}Waiting there for ^{F#}me? ^{.F#} \\
^{.E}Nothing left to ^{F#}want ^{.F#} \\
^{.E}Cashing in my ^{C#}claim to a ^{.B}world, ^{.A}life lived mostly ^{F#}free
\end{chorus} 

\begin{interlude}
\begin{tabular}[t]{@{}lllll}
|_{F#} & |_{.F#} _{B*} _{A*} & |_{F#} & |_{.F#} _{B*} _{A*} & |  \\
|_{F#} & |_{.F#} _{B*} _{A*} & |_{F#} & |_{.F#} _{B*} _{A*} & |  \\
|_{B} & |_{B} & |_{F#} & |_{F#} & |  \\
|_{B} & |_{B} & |_{F#} & |_{.C#} _{.D} & |  \\
\end{tabular}
\\
\instruction{Pause for 2 bars}
\\
\begin{tabular}[t]{@{}lllll}
|_{F#} & |_{C#} & |_{.C#} _{.E} & |_{F#} & |  \\
|_{F#} & |_{C#} & |_{.C#} _{.E} & |_{F#*} & |  \\
\end{tabular}
\\
\instruction{Pause for 2 beats}
\\
\end{interlude}

\begin{chorus}
^{N.\symbol{67}.}On the other ^{F#}side? ^{.F#} \\
^{.E}Waiting there for ^{F#}me? ^{.F#} \\
^{.E}Nothing left to ^{F#}want ^{.F#} \\
^{.E}Cashing in my ^{C#}claim to a ^{.B}world, ^{.A}life lived mostly ^{F#}free ^{.F#} ^{F#*}
\end{chorus}
