\documentclass{skrul-leadsheet}
\setchords{
  major-seven = $\Delta$
}
\begin{document}

\begin{song}[transpose-capo=true]{title={1979}, band={Smashing Pumpkins}, year={1995}, key={E}}

\begin{intro}
\begin{tabular}[t]{@{}lllll}
| _{Emaj7} & | _{E} & | _{Asus2} & |  _{Asus2} & |
\end{tabular}
\end{intro}

\begin{verse}
^{Emaj7} ^{E} ^{Asus2} Shakedown nineteen seventy nine,
^{Emaj7} ^{E} ^{Asus2} Cool kids never have the time.  \\
^{Emaj7} ^{E} On a ^{Asus2}live wire right up off the ^{F#m7}street,
You and ^{B}I should meet. 
\end{verse}

\begin{verse}
^{Emaj7} ^{E} ^{Asus2} Junebug skippin’ like a stone
^{Emaj7} ^{E} ^{Asus2} Headlights pointed at the dawn. \\
^{Emaj7} ^{E} ^{Asus2} We were sure we'd never see an ^{F#m7}end to it ^{B}all.
\end{verse}

\begin{chorus}
And ^{E}I----- don't ^{Emaj7}even ^{Amaj7}care to shake these zipper ^{E}blues, \\
And ^{Emaj7}we don't ^{Amaj7}know just where our bones will ^{E}r-e-s-t to ^{Emaj7}dust I  ^{Amaj7}guess \\
Forgotten and ^{F#m7}absorbed into the ^{B}earth bel^{(Emaj7)}ow.
\end{chorus}

\begin{interlude}
\begin{tabular}[t]{@{}lllll}
| _{Emaj7} & | _{E} & | _{Asus2} & |  _{Asus2} & |
\end{tabular}
\end{interlude}

\begin{verse}
^{Emaj7} ^{E} ^{Asus2} Double cross the vacant and the bored,
^{Emaj7} ^{E} ^{Asus2} They're not sure just what we have in store. \\
^{Emaj7} ^{E} ^{Asus2} Morphine city slippin' ^{F#m7}dues down to ^{B}see
\end{verse}

\begin{chorus}
That ^{E}weeeeee don't ^{Emaj7}even  ^{Amaj7}care as restless as we ^{E}are, \\
We ^{Emaj7}feel the ^{Amaj7}pull in the land of a thousand ^{E}g-u-i-l-t-s and ^{Emaj7}poured ce-^{Amaj7}ment, \\
Lamented and ^{(B)}assured
\end{chorus}

\begin{bridge}
^{B}To the lights and ^{C#m}town be^{A}low,
^{B}Faster than the ^{C#m}speed of s^{A}ound, \\
^{B}Faster than we t^{C#m}hought we'd go ^{A}
be^{F#m7}neath the ^{B}sound   of ^{(Emaj7)}hope.
\end{bridge}

\begin{verse}
^{Emaj7} ^{E} ^{Asus2} Justine never knew the rules,
^{Emaj7} ^{E} ^{Asus2} Hung down with the freaks and ghouls. \\
^{Emaj7} ^{E} No a-^{Asus2}pologies ever need be made,
^{Emaj7} ^{E} ^{Asus2} I know better than you ^{F#m7}fake it to ^{B}see
\end{verse}

\begin{chorus}
That ^{E}weeeeee don't ^{Emaj7}even ^{Amaj7}care
to shake these zipper ^{E}blues, \\
And ^{Emaj7}we don't ^{Amaj7}know just where our bones will
^{E}R-e-s-t to ^{Emaj7}dust I ^{Amaj7}guess, \\
Forgotten and a^{F#m7}bsorbed into the ^{B}earth below. ^{(E)}
\end{chorus}

\begin{outro}
^{Emaj7} ^{E} ^{Asus2} The street heats the urgency of now.
^{Emaj7} ^{E} ^{Asus2} As you see there's no-one a-round. ^{E}
\end{outro}

\end{song}
\end{document}
