\documentclass{skrul-leadsheet}
\begin{document}
\begin{song}[transpose-capo=true]{title={Senses Working Overtime}, band={XTC}, year={1982}, key={E -> F}}

\begin{intro}
\begin{tabular}[t]{@{}lllll}
|_{G#m} & |_{F#} & |_{G#m} & |_{F#} & | \instruction{Repeat 2x} \\
\end{tabular}
\end{intro}

\begin{verse}
^{G#m}Hey, ^{F#}hey, the ^{G#m}clouds are ^{F#}whey.  There's ^{G#m}straw for the ^{F#}donkeys \\
And the ^{G#m}innocents can ^{F#}all sleep s^{C#m}afely, ^{G#m} ^{C#m} ^{G#m}all sleep ^{C#m}safely. ^{G#m} ^{C#m} ^{G#m}  \\

^{G#m}My, ^{F#}my, ^{G#m}sun is ^{F#}pie.  There's ^{G#m}fodder for the ^{F#}cannons \\
And the ^{G#m}guilty ones can ^{F#}all sleep s^{C#m}afely,  ^{G#m} ^{C#m} ^{G#m}all sleep ^{C#m}safely. ^{G#m} ^{C#m} ^{G#m}
\end{verse}
 
\begin{prechorus}
^{A} And all the ^{Asus4}world is football-^{A}shaped, it's just for ^{Asus4}me to kick in sp^{B}ace \\
And I can ^{Bsus4}see, hear, smell, touch, ^{B}taste
\end{prechorus}

\begin{chorus}
And I've got ^{E*}one, ^{E*}two, ^{B*}three, ^{B*}four, ^{E*}five senses working ^{A}o - ^{E}ver - ^{B}time. \\
^{A}Trying to ^{B}take this ^{E}all in. \\
^{B}I've got ^{E*}one, ^{E*}two, ^{B*}three, ^{B*}four, ^{E*}five senses working ^{A}o - ^{E}ver - ^{B}time. \\
^{A}Trying to taste the ^{B}difference between a ^{A}lemon and a ^{B}lime \\
^{A}Pain and ^{B}pleasure and the ^{E}church bells softly ^{E}chime.
\end{chorus}

\begin{interlude}
\begin{tabular}[t]{@{}lllll}
|_{G#m} & |_{F#} & |_{G#m} & |_{F#} & | \instruction{Repeat 2x} \\
\end{tabular}
\end{interlude}

\begin{verse}
^{G#m}Hey, ^{F#}hey, ^{G#m}night fights ^{F#}day.  There's ^{G#m}food for the ^{F#}thinkers \\
And the ^{G#m}innocents can ^{F#}all live s^{C#m}lowly, ^{G#m} ^{C#m} ^{G#m}all live ^{C#m}slowly. ^{G#m} ^{C#m} ^{G#m} \\

^{G#m}My, ^{F#}my, the ^{G#m}sky will ^{F#}cry.  ^{G#m}Jewels for the ^{F#}thirsty \\
And the ^{G#m}guilty one's can ^{F#}all die s^{C#m}lowly,  ^{G#m} ^{C#m} ^{G#m}all die ^{C#m}slowly. ^{G#m} ^{C#m} ^{G#m}
\end{verse} 

\begin{prechorus}
^{A} And all the ^{Asus4}world is biscuit-^{A}shaped, it's just for ^{Asus4}me to feed my ^{B}face \\
And I can ^{Bsus4}see, hear, smell, touch, ^{B}taste
\end{prechorus}

\begin{chorus}
\instruction{Repeat Chorus}
\end{chorus}

\newpage

\begin{bridge}
\begin{tabular}[t]{@{}lllll}
|_{A} & |_{G} & |_{A} & |_{G} & | \instruction{Repeat 2x} \\
\end{tabular}

^{A} And ^{G}birds might   ^{A}fall from ^{G}black skies ^{A} ^{G} Whoo! ^{A}Whoo! ^{G}  \\
^{A} And ^{G}bullies might ^{A}give you  ^{G}black eyes  ^{A} ^{G} Whoo! ^{A}Whoo! ^{G}  \\
^{A} And ^{G}buses might   ^{A}skid on   ^{G}black ice   ^{A} ^{G} Whoo! ^{A}Whoo! ^{G}  \\
^{A} But, to ^{G}me, they're ^{A}very,   ^{G}very... \\\
^{D}Beau - ^{A}u - ^{D}ti - f^{A}ul! ^{Bb}   (^*{F}Eng ^{Bb}land's ^{F}glory!) \\
^{D}Beau - ^{A}u - ^{D}ti - f^{A}ul! ^{Bb}   (^{F}A s^{Bb}tri - ^{F}king beauty!) \\

^{D}Doo-doo-doo-doo!    Doo-doo-doo-doo!  Doo-doo-doo! \\
^{Bb}Doo-doo-doo-doo!    Doo-doo-doo-doo!  Doo-doo-doo! \\
^{D}Doo-doo-doo-doo!    Doo-doo-doo-doo!  Doo-doo-doo! \\
^{Bb}Doo-doo-doo-doo!  D^{F}oo-doo-doo-doo! \\
\end{bridge}
 
\begin{prechorus}
^{Bb}And all the ^{Bbsus4}world is football-shape^{Bb}d, it's just for ^{Bbsus4}me to kick in spa^{C}ce \\
And I can ^{Csus4}see, hear, smell, touch, ^{C}taste
\end{prechorus}
 
 
\begin{chorus}
And I've got ^{F*}one, ^{F*}two, ^{C*}three, ^{C*}four, ^{F*}five senses working ^{Bb}o - ^{F}ver – ^{C}time. \\
^{Bb}Trying to ^{C}take this ^{F}all in. \\
^{C}I've got ^{F*}one, ^{F*}two, ^{C*}three, ^{C*}four, ^{F*}five senses working ^{Bb}o - ^{F}ver – ^{C}time. \\
^{Bb}Trying to taste the ^{C}difference between the ^{Bb}goods and ^{C}crime, ^{Bb}dirt or ^{C}treasure. \\

 And there's ^{F*}one, ^{F*}two, ^{C*}three, ^{C*}four, ^{F*}five senses working ^{Bb}o - ^{F}ver – ^{C}time. \\
^{Bb}Trying to ^{C}take this ^{F}all in. \\
^{C}I've got ^{F*}one, ^{F*}two, ^{C*}three, ^{C*}four, ^{F*}five senses working ^{Bb}o - v^{F}er – ^{C}time. \\
^{Bb}Trying to taste the ^{C}difference between the ^{Bb}lemon and ^{C}lime. \\
^{Bb}Pain and ^{C}pleasure and the ^{F*}church bells softly chime. \\
\end{chorus} 

\end{song}
\end{document}