\documentclass{skrul-leadsheet}

\begin{document}

\begin{song}[transpose-capo=true]{title={Great DJ}, band={The Ting Tings}, year={2008}, key={D}}

\begin{intro}
\begin{tabular}[t]{@{}lllll}
|_{D} & |_{D+} & |_{D} & |_{D+} & |  4x \\
\end{tabular}
\end{intro}

\begin{verse}
^{D}Fed up with your indiges^{D+}tion, ^{D}swallow worries one by ^{D+}one \\
^{D}Folks got high at a ^{D+}quarter to five, don't you ^{D}feel you're growing up ^{D+}undone \\
^{D}Nothing but the local D^{D+}J., He ^{D}said he had some songs to ^{D+}play \\
^{D}What went down from his fooling ^{D+}around, gave ^{D}hope and a brand new ^{D+}day
\end{verse}

\begin{chorus}
\begin{tabbing}
^{N.C.}Imagine all the ^{Dm}girls, ah ah, ah, ah, ^{Am}ah, ah, ah, ah. \space\space\space\space\space\space\space\space\space\space\space \=  And the ^{Dm}boys, ah ah, ah, ah, ^{Am}ah, ah, ah, ah. \\
And the ^{Dm}strings, eee, eee, eee, eee, ^{Am}eee, eee, eee, eee. \> And the ^{Dm}drums, the drums, the ^{Am}drums, the drums, \\
The ^{D5}drums, the drums, the ^{D5}drums, the drums, the ^{D5}drums, the drums, the ^{D5}drums, the drums, oh!
\end{tabbing}
\end{chorus}

\begin{interlude}
\begin{tabular}[t]{@{}lllll}
|_{D} & |_{D+} & |_{D} & |_{D+} & | \\
\end{tabular}
\end{interlude}
 
\begin{verse}
^{D}Nothing was the same a^{D+}gain, ^{D}all about where and ^{D+}when \\
^{D}Blowing our minds in our ^{D+}life unkind, you ^{D}gotta love the BP^{D+}M \\
^{D}When his work was all but ^{D+}done, re^{D}membering how this be^{D+}gun \\
^{D}We wore his love like a ^{D+}hand in a glove, this ^{D}preacher plays it all night ^{D+}long.
\end{verse}

\begin{chorus}
\begin{tabbing}
^{N.C.}Nothing but the ^{Dm}girls, ah ah, ah, ah, ^{Am}ah, ah, ah, ah. \space\space\space\space\space\space\space\space\space\space\space \=  And the ^{Dm}boys, ah ah, ah, ah, ^{Am}ah, ah, ah, ah. \\
And the ^{Dm}strings, eee, eee, eee, eee, ^{Am}eee, eee, eee, eee. \> And the ^{Dm}drums, the drums, the ^{Am}drums, the drums, \\
The ^{D}drums, the drums, the ^{D7sus}drums, the drums, the ^{D}drums, the drums, the ^{D7sus}drums, the drums, \\
The ^{D}drums, the drums, the ^{D7sus}drums, the drums, the ^{D}drums, the drums, the ^{D7sus}drums, the drums
\end{tabbing}
\end{chorus}

\begin{interlude}
\begin{tabular}[t]{@{}lllll}
|_{Dm} & |_{Am} & |_{Dm} & |_{Am} & | 2x \\
\end{tabular}
\end{interlude}

\begin{chorus}
\begin{tabbing}
^{(Am)}Imagine all the ^{Dm}girls, ah ah, ah, ah, ^{Am}ah, ah, ah, ah. \space\space\space\space\space\space\space\space\space\space\space \=  And the ^{Dm}boys, ah ah, ah, ah, ^{Am}ah, ah, ah, ah. \\
And the ^{Dm}strings, eee, eee, eee, eee, ^{Am}eee, eee, eee, eee. \> And the ^{Dm}drums, ah ah, ah, ah, ^{Am}ah, ah, ah, ah. \\
All the ^{Dm}girls, ah ah, ah, ah, ^{Am}ah, ah, ah, ah.  \> And the ^{Dm}boys, ah ah, ah, ah, ^{Am}ah, ah, ah, ah. \\
And the ^{Dm}strings, eee, eee, eee, eee, ^{Am}eee, eee, eee, eee. \> And the ^{Dm}drums, the drums, the ^*{Am}drum ^{-}s, ^{N.C.}the drums, \\
\end{tabbing}
\end{chorus}

\end{song}
\end{document}
