\documentclass{skrul-leadsheet}
\usepackage{graphicx}
\begin{document}
\begin{song}[transpose-capo=true]{title={The Chanukah Song}, band={Adam Sandler}, year={1995}, key={A}}

\begin{chorus}
^{A}Put on your ^{E}yarmulke, ^{D}here comes ^{E}Chanukah, it's ^{A}so much ^{E}fun-akah, to ^{D}celebrate ^{E}Chanukah
\end{chorus} 

\begin{verse}
^{A*}Chanukah ^{E*}is the ^{D*}festival of ^{E*}lights, ^{A*}Instead of one day of ^{E*}presents, we have ^{D*}eight crazy ^{E*}nights \\
\scalebox{0.91}[1.0]{^{A*}When you feel like the only ^{E*}kid in town with^{D*}out a Christmas ^{E*}tree,  ^{A*}here's a list of people who are ^{E*}Jewish, ^{D*}just like you and ^{E*}me: \space }
\end{verse}

\begin{verse}
^{A}David Lee ^{E}Roth ^{D}lights the me^{E}norah, ^{A}so do James ^{E}Caan, Kirk Douglas, and the ^{D}late Dinah ^{E}Shore-ah \\
^{A} Guess who eats to^{E}gether at the ^{D}Carnegie ^{E}Deli? ^{A} Bowzer from ^{E}Sha Na Na, and ^{D}Arthur Fonzer^{E}relli \\
^{A*}Paul Newman's half ^{E*}Jewish; ^{D*}Goldie Hawn's half ^{E*}too, ^{A}put them to^{E}gether, what a ^{D}fine lookin' ^{E}Jew! ^{Esus4} ^{-} ^{E}
\end{verse} 

\begin{prechorus}
You ^{D}don't need "Deck the Halls" or "^{D}Jingle Bell Rock" \\
Cause ^{E}you can spin the dreidel with Captain ^{E}Kirk and Mr. Spock -- both Jewish! ^{E9!}
\end{prechorus} 

\begin{chorus}
^{A}Put on your ^{E}yarmulke, it's ^{D}time for ^{E}Chanukah, \\
The ^{A}owner of the Seattle Super^{E}sonic-ahs ^{D}celebrates ^{E}Chanukah. \\
^{A} O.J. ^{E}Simpson, ^{D*}not a ^{N.C.}Jew! \\
^{A} But guess who ^{E}is, Hall of ^{D}Famer Rod Care^{E*}w (he converted!^{E9!})
\end{chorus} 

\begin{verse}
^{A}We got Ann ^{E}Landers and her ^{D}sister Dear A^{E}bby, ^{A} Harrison Ford's a ^{E}quarter Jewish, ^{D}not too ^{E}shabby! \\
^{A}Some people ^{E}think that ^{D}Ebenezer ^{E}Scrooge is, ^{A} well, he's not, but ^{E}guess who is: ^{D}all Three ^{E}Stooges ^{Esus4} ^{-} ^{E}
\end{verse}
 
\begin{prechorus}
^{D}So many Jews are ^{D}in show biz \\
^{E}Tom Cruise isn't, but I ^{E*}heard his agent is ^{E9!}
\end{prechorus} 

\begin{outro}
\scalebox{0.97}[1.0]{^{A}Tell your friend Ver^{E}onica, it's ^{D}time you celebrate ^{E}Chanukah, I ^{A}hope I get a har^{E}monica, on this ^{D}lovely, lovely ^{E}Chanukah \space} \\
So ^{A}drink your gin and ^{E}tonic-ah, and ^{D}smoke your mari^{E}juana-kah, If you ^{A}really, really ^{E}wanna-kah, have a ^{D*}happy, happy, ^{E*}happy, happy \\
^{A*}Chanukah. Happy Chanukah! \\
\end{outro}

\end{song}
\end{document}