\documentclass{skrul-leadsheet}
\begin{document}
\begin{song}[transpose-capo=true]{title={Texarkana}, band={R.E.M.}, year={1991}, key={Em}, tempo={144}}

\begin{intro}
\begin{tabular}[t]{@{}lllll}
|_{Em} & |_{G} & |_{Bm} & |_{Bm} & | \\
|_{Em} & |_{A} & |_{G} & |_{G} & | \instruction{Repeat 2x}
\end{tabular}	 
\end{intro}

\begin{verse}
^{Em}20,000 ^{G}miles to an ^{Bm}oasis, ^{Bm} \hspace{20pt}
^{Em}20,000 ^{A}years will I ^{G}burn. ^{G} \\
^{Em}20,000 ^{G}chances I ^{Bm}wasted, ^{Bm}  \hspace{20pt}
^{Em}waiting for the ^{A}moment to ^{G}turn. ^{G}
\end{verse} 

\begin{chorus}
^{Cadd9}I would give my ^{D}life to find it, ^{Bm}I would give it all. ^{Bm} \\
^{Cadd9}Catch me if I ^{Am*}fall.
\end{chorus} 

\begin{postchorus}
\begin{tabular}[t]{@{}lllll}
|_{Em} & |_{.D} _{Dsus2*} _{D*} & |_{Em} & |_{.D} _{Dsus2*} _{D*} & | \\
\end{tabular}
\end{postchorus}

\begin{verse}
^{Em}Walking through the ^{G}woods, I have ^{Bm}faced it,
^{Em} looking for ^{A}something to ^{G}learn. \\
^{Em}30,000 ^{G}thoughts have re^{Bm}placed it,
^{Em}Never in my ^{A}time to re^{G}turn.
\end{verse} 

\begin{chorus}
^{Cadd9}I would give my ^{D}life to find it, ^{Bm}I would give it all. ^{Bm} \\
^{Cadd9}Catch me if I ^{Am*}fall.
\end{chorus} 

\begin{postchorus}
\begin{tabular}[t]{@{}lllll}
|_{Em} & |_{.D} _{Dsus2*} _{D*} & |_{Em} & |_{.D} _{Dsus2*} _{D*} & | \\
\end{tabular}
\end{postchorus}

\begin{bridge}
\begin{tabular}[t]{@{}lllll}
|_{Asus2} & |_{Asus2} & |_{G} & |_{G} & | \\
|_{Asus2} & |_{Asus2} & |_{G} & |_{G} & | \\
\end{tabular}
\\
\\
All a^{D}lone, ^{D} ^{G} ^{G}waiting to ^{D}fall ^{D} ^{E} ^{E*}
\end{bridge}

\begin{verse}
^{Em}40,000 ^{G}stars in the ^{Bm}evening,
^{Em} look at them ^{A}fall from the ^{G}sky. \\
^{Em}40,000 ^{G}reasons for ^{Bm}living,
^{Em}40,000 ^{A}tears in your ^{G}eye. \\
\end{verse} 

\begin{chorus}
^{Cadd9}I would give my ^{D}life to find it, ^{Bm}I would give it all. ^{Bm} \\
^{Cadd9}Catch me if I ^{Am*}fall.
\end{chorus} 

\begin{outro}
^{Em} ^{.D} ^{Dsus2*} ^{D*} \hspace{20pt} ^{Em} ^{.D}Catch me ^{Dsus2}if ^{D*}I ^{(Em)}fall. \\
^{Em} ^{.D} ^{Dsus2*} ^{D*} \hspace{20pt} ^{Em} ^{.D}Catch me ^{Dsus2}if ^{D*}I ^{(Em)}fall. \\
^{Em}Catch me if I ^*{.D}fa ^{Dsus2*}ll ^{D*}  \instruction{Repeat 5x} \\
^{Em}Catch me if I ^{D*}fall.

\end{outro}
 
\end{song}
\end{document}